Energy aware HPC

### 2021-03-25 thesis/experiments/experiments.tex
first version

\begin {figure} [H]
\centering
\begin{subfigure}[t]{0.5\textwidth}
\centering
\includegraphics[height= 7.5cm]{intro/Imagens/c_states}
\caption {C states}
\end {subfigure}%
~
\begin{subfigure}[t]{0.5\textwidth}
\centering
\includegraphics[height= 7.5cm]{intro/Imagens/p_states}
\caption {States P}
\end {subfigure}
\caption {Illustration of states C and P} {Altered image from \protect \url {https://www.thomas-krenn.com/en/wiki/Processor_P-states_and_C-states}}
\label {fig: p_state}
\end {figure}

@@

\begin {figure} [H]
\centering
\includegraphics [height = 7.5cm] {intro/Imagens/IPMI-Block-Diagram.png}
\caption {IMPI diagram} {Image taken from \protect \url {https://pt.wikipedia.org/wiki/Intelligent_Platform_Management_Interface}, the main components of IPMI and how they communicate are shown}
\label {fig: IPMI}
\end {figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{models/figures/hypothesis/input_instructions/fp/Blackschole.png}
	\caption{Caption}
	\label{fig:my_label}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{models/figures/hypothesis/input_instructions/fp/Canneal.png}
	\caption{Caption}
	\label{fig:my_label}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{models/figures/hypothesis/input_instructions/input_time/Blackschole.png}
	\caption{Caption}
	\label{fig:my_label}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{models/figures/hypothesis/input_instructions/input_time/Canneal.png}
	\caption{Caption}
	\label{fig:my_label}
\end{figure}

@@

\subsubsection{Validation}
The validation results for each application trained with 10 random configurations are displayed in figure \ref{fig:mpe_svr_eq} and the raw MPE values in  table~\ref{tab:mpe_svr_eq}.
\begin{figure}[htb!]
	\includegraphics[width=\columnwidth]{models/figures/mpe_svr_eq.png}
	\caption{Comparison of the Mean Percentage Error between the proposed model and SVR. "Model mean" and "SVR mean" are the average of all MPE values for all applications.
	}
	\label{fig:mpe_svr_eq}
\end{figure}
\begin{table}[htb!]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Application  & Model & SVR   \\ \hline
		Ferret       & 5.25     & 12.49  \\ \hline
		Raytrace     & 6.36     & 11.95  \\ \hline
		Fluianimate  & 2.44     & 22.90  \\ \hline
		x264         & 8.28     & 15.33  \\ \hline
		Vips         & 7.54     & 10.80  \\ \hline
		Swaptions    & 6.54     & 18.57  \\ \hline
		Canneal      & 3.12     & 6.13   \\ \hline
		Dedup        & 8.85     & 13.70  \\ \hline
		Freqmine     & 2.44     & 3.24   \\ \hline
		Blackscholes & 2.18     & 11.00  \\ \hline
		HPL          & 7.47     & 12.75  \\ \hline
		Bodytrack    & 16.98    & 34.12  \\ \hline
		Openmc       & 11.15    & 24.34  \\ \hline
	\end{tabular}
	\caption{Comparison of the Mean Percentage Error between the proposed model and SVR: raw values.}
	\label{tab:mpe_svr_eq}
\end{table}

@@

Figure \ref{fig:overheadFerretVips} shows the comparisons of MPE and energy spent to create each model for two selected applications. According to the results, the analytical model is found to be very stable, not changing much as more data is added, while the SVR keeps reshaping to adapt to the data. 
The error of the analytical model is almost constant but that of  the SVR, initially very high, drops at some point.
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.44\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/overhead/overall.png}}
		\caption{Average energy spent on all applications during model creation. The two curves are identical because the same data were used to adjust the SVR and the model.}
		\label{fig:overall_overhead}
	\end{subfigure}
	%
	\quad
	\begin{subfigure}[b]{0.44\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/overhead/overall_mpe.png}}
		\caption{
			MPE all applications: SVR needs 10 times more data to have an MPE lower than the model.}
		\label{fig:overall_MPE}
	\end{subfigure}
	\caption{Overall results for energy and MPE for each training size.}
	\label{fig:overall_train}
\end{figure}
Figure \ref{fig:overall_train} presents the overall results, with the mean energy overhead and MPE for all applications.
The meeting point of the MPE for the SVR and the proposed model can be extracted from  \ref{fig:overall_MPE}.
There it shows that around 90 configurations the SVR starts to have a smaller error. The cost of that is the linear increase in energy spent on training. The increase in energy, about 10 times more, can be observed in Figure \ref{fig:overall_overhead}.

>>>>

\begin {figure} [H]
\centering
\begin{subfigure}[t]{0.5\textwidth}
\centering
\includegraphics[height= 7.5cm]{intro/figures/c_states}
\caption {C states}
\end {subfigure}%
~
\begin{subfigure}[t]{0.5\textwidth}
\centering
\includegraphics[height= 7.5cm]{intro/figures/p_states}
\caption {States P}
\end {subfigure}
\caption {Illustration of states C and P} {Altered image from \protect \url {https://www.thomas-krenn.com/en/wiki/Processor_P-states_and_C-states}}
\label {fig: p_state}
\end {figure}

@@

\begin {figure} [H]
\centering
\includegraphics [height = 7.5cm] {intro/figures/IPMI-Block-Diagram.png}
\caption {IMPI diagram} {Image taken from \protect \url {https://pt.wikipedia.org/wiki/Intelligent_Platform_Management_Interface}, the main components of IPMI and how they communicate are shown}
\label {fig: IPMI}
\end {figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{models/figures/hypothesis/input_instructions/fp/blackscholes.png}
	\caption{Caption}
	\label{fig:my_label}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{models/figures/hypothesis/input_instructions/fp/canneal.png}
	\caption{Caption}
	\label{fig:my_label}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{models/figures/hypothesis/input_instructions/input_time/blackscholes.png}
	\caption{Caption}
	\label{fig:my_label}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{models/figures/hypothesis/input_instructions/input_time/canneal.png}
	\caption{Caption}
	\label{fig:my_label}
\end{figure}

@@

\subsubsection{Validation}
The validation results for each application trained with 10 random configurations are displayed in figure \ref{fig:mpe_svr_eq} and the raw MPE values in  table~\ref{tab:mpe_svr_eq}.
\begin{figure}[htb!]
	\includegraphics[width=\columnwidth]{models/figures/mae_svr_eq.png}
	\caption{Comparison of the Mean Percentage Error between the proposed model and SVR. "Model mean" and "SVR mean" are the average of all MPE values for all applications.
	}
	\label{fig:mpe_svr_eq}
\end{figure}
\begin{table}[htb!]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		Application  & Model & SVR   \\ \hline
		Ferret       & 5.25     & 12.49  \\ \hline
		Raytrace     & 6.36     & 11.95  \\ \hline
		Fluianimate  & 2.44     & 22.90  \\ \hline
		x264         & 8.28     & 15.33  \\ \hline
		Vips         & 7.54     & 10.80  \\ \hline
		Swaptions    & 6.54     & 18.57  \\ \hline
		Canneal      & 3.12     & 6.13   \\ \hline
		Dedup        & 8.85     & 13.70  \\ \hline
		Freqmine     & 2.44     & 3.24   \\ \hline
		Blackscholes & 2.18     & 11.00  \\ \hline
		HPL          & 7.47     & 12.75  \\ \hline
		Bodytrack    & 16.98    & 34.12  \\ \hline
		Openmc       & 11.15    & 24.34  \\ \hline
	\end{tabular}
	\caption{Comparison of the Mean Percentage Error between the proposed model and SVR: raw values.}
	\label{tab:mpe_svr_eq}
\end{table}

@@

Figure \ref{fig:overheadFerretVips} shows the comparisons of MPE and energy spent to create each model for two selected applications. According to the results, the analytical model is found to be very stable, not changing much as more data is added, while the SVR keeps reshaping to adapt to the data. 
The error of the analytical model is almost constant but that of  the SVR, initially very high, drops at some point.
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.44\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/overhead/overall_energy_10pts.png}}
		\caption{Average energy spent on all applications during model creation. The two curves are identical because the same data were used to adjust the SVR and the model.}
		\label{fig:overall_overhead}
	\end{subfigure}
	%
	\quad
	\begin{subfigure}[b]{0.44\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/overhead/overall_mpe_10pts.png}}
		\caption{
			MPE all applications: SVR needs 10 times more data to have an MPE lower than the model.}
		\label{fig:overall_MPE}
	\end{subfigure}
	\caption{Overall results for energy and MPE for each training size.}
	\label{fig:overall_train}
\end{figure}
Figure \ref{fig:overall_train} presents the overall results, with the mean energy overhead and MPE for all applications.
The meeting point of the MPE for the SVR and the proposed model can be extracted from  \ref{fig:overall_MPE}.
There it shows that around 90 configurations the SVR starts to have a smaller error. The cost of that is the linear increase in energy spent on training. The increase in energy, about 10 times more, can be observed in Figure \ref{fig:overall_overhead}.
